---
title: "Speed-acc-novel Paper Vizsualizations"
output: html_document
---

# Set up

```{r set up}
source(here::here("code/helper_functions/libraries_and_functions.R"))
source(here::here("code/helper_functions/permutation_helpers.R"))
source(here::here("code/helper_functions/ewma_helper_funs.R"))
source(here::here("code/helper_functions/paper_helpers.R"))

data_path <- "data/03_processed_data/novel_words"
image_path <- "writing/figures/plots"
```

# Read and process data

```{r}
file_name <- "speed_acc_novel_timecourse.feather"
d <- read_feather(here::here(data_path, file_name)) 
```

Filter based on exlcusions in the subject log and remove bad blocks based on subject log.

```{r}
d_analysis <- d %>% 
  filter(keep_drop == "keep",
         t_rel_noun >= 0, 
         t_rel_noun <= 3
  )
```

Create time bins for each participant and each trial. 

```{r}
d_analysis %<>% 
  split(.$subid) %>%  
  purrr::map_dfr(create_time_bins_ss, t_ms_diff = 33)
```

Create exclusions table.

```{r}
# based on runsheet information
d_exclusions_rs <- d %>% 
  distinct(subid, keep_drop, reason_excluded, age_category) %>% 
  filter(keep_drop == "drop") 

# based on number of trials completed.
d_exclusions_et <- d_analysis %>%
  filter(target_looking != "away") %>% 
  distinct(subid, trial_num_exp, age_category) %>% 
  count(subid, age_category) %>% 
  filter(n < 16) %>% 
  mutate(keep_drop = "drop", 
         reason_excluded = "fewer than half trials completed") 

# create subid vector for filtering later
ss_exclude <- d_exclusions_et %>% pull(subid)

# Join exclusions tables and save to disk.
d_exclusions_final <- d_exclusions_et %>% 
  select(-n) %>% 
  bind_rows(d_exclusions_rs)

write_csv(d_exclusions_final, path = here::here("data/03_processed_data/speed_acc_novel_exclusions.csv"))
```

Filter participants who did not complete more than half the trials. 

```{r}
d_analysis %<>% filter(!(subid %in% ss_exclude))
```

Check how many trials in each block.

```{r}
d_analysis %>% 
  distinct(subid, trial_num_exp, learning_block, gaze_condition) %>% 
  count(subid, learning_block, gaze_condition) %>% 
  arrange(n) %>% 
  kable()
```

Make a table of proportion looking to each area of interest: Left, Right, Center, and Away

```{r}
d_analysis %>% 
  filter(!is.na(target_looking)) %>% 
  group_by(target_looking, age_category) %>% 
  summarise(count_looks = n()) %>% 
  group_by(age_category) %>% 
  mutate(total_looks = sum(count_looks),
         prop_looks = round(count_looks / total_looks, 2)) %>% 
  arrange(age_category) %>% 
  kable()
```

Create flag for trials with less than half valid samples.

```{r}
trial_filter <- d_analysis %>% 
  distinct(subid, trial_num_exp, learning_block, gaze_condition, target_looking, time_ms_normalized) %>% 
  count(subid, trial_num_exp, learning_block, gaze_condition, target_looking) %>% 
  group_by(trial_num_exp, subid) %>% 
  mutate(total_samples = sum(n),
         prop_trial = n / total_samples,
         good_trial = case_when(
           target_looking == "away" & prop_trial >= 0.5 ~ "drop",
           TRUE ~ "keep"
         )) %>% 
  distinct(subid, trial_num_exp, good_trial)

d_analysis %<>% left_join(trial_filter)
```

Check how many samples we have for each trial after removing away looks.

```{r}
d_analysis %<>% filter(target_looking != "away")
```

```{r}
n_samples_trial <- d_analysis %>% 
  count(subid, trial_num_exp) %>% 
  rename(n_samples_trial = n)

n_samples_trial %>%   
  ggplot(aes(x = n_samples_trial)) +
  geom_histogram() 

d_analysis %<>% left_join(n_samples_trial)
```

Filter away looks and bad trials (< 50% looking away).

```{r}
d_analysis %<>% 
  filter(good_trial == "keep") %>% 
  filter(n_samples_trial >= 45)
```

# Visualize timecourse looking to all AOIs

```{r}
d_analysis %<>% 
  mutate(age_category = ifelse(age_category == "child", "children", "adults")) %>% 
  mutate(age_category = factor(age_category, levels = c("children", "adults"))) 
```


```{r compute mean gaze onset relative to noun onset}
gaze_onset <- d_analysis %>% 
  distinct(noun_onset_seconds, gaze_onset_seconds) %>% 
  na.omit() %>% 
  mutate(gaze_onset_rel_noun = (gaze_onset_seconds - noun_onset_seconds) * 1000) %>% 
  summarise(m_gaze_onset = mean(gaze_onset_rel_noun))
```

## Aggregate proportion looking as a function of age group and gaze condition

```{r}
ss_groupings <- list("subid", "time_ms_normalized", "gaze_condition", 
                     "trial_type", "age_category", "trial_num_exp")

ms_groupings <- list("subid", "time_ms_normalized", "gaze_condition", 
                     "trial_type", "age_category")

ms_time <- aggregate_ss_looking(d_analysis, ss_groupings, ms_groupings, aoi_column = "target_looking") 

# save graph values for timecourse plot
write_csv(ms_time, here::here(data_path, "speed_acc_novel_tc_gvs.csv"))
```

## Make key timecourse plot

Now make the Tanenhaus style curves for each type of looking.  

```{r make plots}
upper_bound <- 2.5
x_axis_expand <- 1.5

ms_time %<>%
  mutate(target_looking = ifelse(target_looking == "center", "face", target_looking),
         t_sec = time_ms_normalized / 1000) 

# face
san_face_tc <-ms_time %>% 
  filter(t_sec <= upper_bound, target_looking == "face") %>% 
  ggplot(aes(x = as.numeric(t_sec), y = m, 
             color = gaze_condition,
             linetype = age_category)) +
  lims(y = c(0, 0.9),
       x = c(0, upper_bound + x_axis_expand)) +
  geom_line(size=1) +
  guides(color = F, linetype = F) +
  ggthemes::scale_color_ptol() +
  xlab("Time in sec from onset of trial") +
  ylab("Proportion looking") +
  geom_dl(aes(label = age_category), method = "last.bumpup", color = "grey10") +
  theme(legend.position = "top") +
  facet_grid(target_looking~trial_type)

# exposure trials target and distracter
san_exposure_tc <- ms_time %>% 
  filter(t_sec <= upper_bound, target_looking != "face", trial_type == "exposure") %>% 
  ggplot(aes(x = as.numeric(t_sec), y = m, 
             color = gaze_condition,
             linetype = age_category)) +
  lims(#y = c(0, 0.8),
       x = c(0, upper_bound + x_axis_expand)) +
  geom_line(size=1) +
  guides(linetype = F, color = F) +
  ggthemes::scale_color_ptol() +
  xlab("Time in sec from onset of trial") +
  ylab("Proportion looking") +
  geom_dl(aes(label = age_category), method = "last.bumpup", color = "grey10") +
  #geom_hline(yintercept = 0.33, linetype = "dashed") +
  facet_grid(target_looking~trial_type, scales = "free_y")  

# test trials
san_test_tc <- ms_time %>% 
  filter(t_sec <= upper_bound, target_looking != "face", trial_type == "test") %>% 
  ggplot(aes(x = as.numeric(t_sec), y = m, 
             color = gaze_condition,
             linetype = target_looking)) +
  lims(#y = c(0, 0.8),
       x = c(0, upper_bound + x_axis_expand)) +
  geom_line(size=1) +
  labs(color = "Gaze Condition") + 
  guides(linetype = F) +
  ggthemes::scale_color_ptol() +
  xlab("Time in sec from onset of trial") +
  ylab("Proportion looking") +
  geom_dl(aes(label = target_looking), method = "last.bumpup", color = "grey10") +
  #geom_hline(yintercept = 0.33, linetype = "dashed") +
  facet_grid(age_category~trial_type, scales = "free_y")  +
  theme(legend.position = "right") 
```

Merge and save the final timecourse plot

```{r}
speed_acc_nov_tc_final <- cowplot::plot_grid(san_face_tc, san_exposure_tc, san_test_tc,
                                             scale = c(0.9, 0.9, 0.9),
                                             ncol = 3,
                                             rel_widths = c(1.45, 0.9, 1.3), 
                                             labels = c("A", "B"))


ggsave(filename = here::here(image_path, "speed_acc_novel_tc.jpeg"),
       plot = speed_acc_nov_tc_final,
       width = 14,
       height = 4)
```

# How does looking to target change across trials?

```{r}
ss_groupings_tr_num <- list("subid", "gaze_condition", "trial_type", "trial_num_learn_block", "age_category", "trial_num_exp")
ms_groupings_tr_num <- list("subid", "gaze_condition", "trial_type", "trial_num_learn_block", "age_category")

ms_trials <- d_analysis %>% 
  filter(target_looking %in% c("target", "distracter")) %>% 
  aggregate_ss_looking(ss_groupings_tr_num, ms_groupings_tr_num,
                       aoi_column = "target_looking", 
                       use_bootstrap = TRUE, 
                       n_boot = 1000)

# Make key plot of target looking as a function of trial number and trial type.
prop_look_plot <- ms_trials %>% 
  ungroup() %>% 
  filter(target_looking == "target") %>% 
  ggplot(aes(x = trial_num_learn_block, y = mean, 
             color = gaze_condition,
             group = interaction(target_looking, gaze_condition))) +
  geom_hline(yintercept = 0.5, lty = "dashed") +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.2),
                  size = 0.4) +
  geom_line(position = position_dodge(width = 0.2)) +
  labs(x = "Trial Number",
       y = "Prop. looking to target",
       color = "Gaze condition:"
       ) +
  lims(y = c(0, 1.05)) +
  facet_grid(age_category~trial_type) +
  ggthemes::scale_color_ptol() +
  theme(legend.position = "top",
        panel.border = element_rect(colour = "grey", fill=NA, size=1),
        text = element_text(size = 15),
        plot.background=element_blank())

## make same plot collapsing across trial numbers
ss_groupings_cond <- list("subid", "gaze_condition", "trial_type", "age_category", "trial_num_exp")
ms_groupings_cond <- list("subid", "gaze_condition", "trial_type", "age_category")

ms_cond <- d_analysis %>% 
  filter(target_looking != "center") %>% 
  aggregate_ss_looking(ss_groupings_cond, ms_groupings_cond,
                       aoi_column = "target_looking", 
                       use_bootstrap = TRUE, 
                       n_boot = 1000) 
# Plot
aggregated_acc_plot <- ms_cond %>% 
  filter(target_looking == "target") %>% 
  ggplot(aes(x = trial_type, y = mean, 
             color = gaze_condition,
             group = interaction(gaze_condition))) +
  geom_hline(yintercept = 0.5, lty = "dashed") +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.2),
                  size = 0.4) +
  geom_line(position = position_dodge(width = 0.2)) +
  lims(y = c(0.1, 1.1)) +
  labs(x = "Trial Type", y = "Prop. Looking Target", color = "Gaze Condition:") + 
  facet_grid(~age_category) +
  guides(color = F) +
  ggthemes::scale_color_ptol() +
  theme(text = element_text(size = 15),
        panel.border = element_rect(colour = "grey", fill=NA, size=1),
        plot.background=element_blank())
```

```{r save-plot}
acc_plot_final <- cowplot::plot_grid(prop_look_plot, aggregated_acc_plot,
                                     scale = c(0.95, 0.85),
                                     ncol = 2,
                                     rel_widths = c(1, 0.9), 
                                     labels = c("A", "B"))

ggsave(plot = acc_plot_final, 
          filename = here::here('writing/figures/plots/speed_acc_novel_proplook.jpeg'),
          width = 12,
          height = 5
          )
```

# Proportion Looking to speaker's face

## How does looking to the speaker change across trials within learning block?

```{r}
ss_groupings_tr_num_center <- list("subid", "gaze_condition", "trial_type", "age_category", "trial_num_exp", "trial_num_learn_block")
ms_groupings_tr_num_center <- list("subid", "gaze_condition", "trial_type", "age_category", "trial_num_learn_block")

ms_trial_num_center <- d_analysis %>% 
  aggregate_ss_looking(ss_groupings_tr_num_center, ms_groupings_tr_num_center,
                       aoi_column = "target_looking", 
                       use_bootstrap = TRUE, 
                       n_boot = 1000) 

# Make key plot of target looking as a function of trial number and trial type.
speaker_look_plot <- ms_trial_num_center %>% 
  ungroup() %>% 
  mutate(age_category = factor(age_category, levels = c("children", "adults"))) %>% 
  filter(target_looking == "center", trial_type == "exposure") %>% 
  ggplot(aes(x = trial_num_learn_block, y = mean, 
             #lty = as.factor(gaze_block),
             color = gaze_condition,
             group = interaction(target_looking, gaze_condition))) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.2)) +
  geom_line(position = position_dodge(width = 0.2)) +
  labs(x = "Trial Number",
       y = "Prop. looking to speaker",
       color = "Gaze condition:"
       ) +
  lims(y = c(0, 0.9)) +
  facet_grid(trial_type~age_category) +
  geom_hline(yintercept = 0.33, lty = "dashed") +
  ggthemes::scale_color_ptol() +
  theme(legend.position = "top",
        panel.border = element_rect(colour = "grey", fill=NA, size=1),
        text = element_text(size = 15))
```

```{r}
ggsave(plot = speaker_look_plot, 
          filename = here::here('writing/figures/plots/speed_acc_novel_speaker_look.jpeg'),
          width = 8,
          height = 6.5
          )
```

