---
title: "Speed-Acc Visualize EWMA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=F, warning=F, cache=F, message=F, sanitize = T, fig.height=6, fig.width=6)
```

```{r}
library(here)
ewma.path <- "data/3_final_merged_data/ewma_output/"
plot.save.path <- "paper/figs/"
```

```{r}
source(here::here("R/helper_functions/libraries_and_functions.R"))
source(here::here("R/helper_functions/ewma_helper_funs.R"))
```

## Read data

```{r read data}
files <- dir(path = ewma.path, pattern = "*.csv") 

# read in all files using purrr
d <- files %>% purrr::map_df(read_ewma, path = ewma.path)
```

## Visualize EWMA results: control charts

Make all the control charts. 

```{r}
ewma_control_charts_trio <- d %>% 
  filter(rt <= 1.5, experiment == "trio") %>% 
  split(.$experiment) %>% 
  purrr::map(.f = aggregate_ewma) %>% 
  purrr::map(.f = plot_ewma_chart)
```

```{r}
ewma_control_charts <- d %>% 
  filter(rt <= 1.2, experiment != "trio") %>% 
  split(.$experiment) %>% 
  purrr::map(.f = aggregate_ewma) %>% 
  purrr::map(.f = plot_ewma_chart)
```

### Experiment 1: Trio (kids)

```{r kid_ewma}
ewma_control_charts_trio$trio
```

#### Area under the curve analysis. So we can compare to the boxplots.

```{r}
ms <- d %>% 
  filter(rt <= 1.5, experiment == "trio") %>% 
  split(.$experiment) %>% 
  purrr::map(.f = aggregate_ewma) 

asl_cut <- ms$trio$cutoff_summary$min_cut[2]
face_cut <- ms$trio$cutoff_summary$min_cut[6]

d_guess <- ms$trio$ewma_summary %>% 
  filter(condition %in% c("ASL", "Face"))
```

```{r}
curves_plot <- d_guess %>% 
  ggplot(aes(x = rt, y = mean_param, color = ewma_param, linetype = condition)) +
  geom_line() +
  ylim(0.3, 0.8)
```
 
Now compute the area between the UCL and CS curves. approach using pracma package (https://stackoverflow.com/questions/4954507/calculate-the-area-under-a-curve)

```{r}
library(pracma)

rt_asl <- d_guess %>% 
  filter(ewma_param == "cs", condition == "ASL", rt <= asl_cut) %>% 
  pull(rt)

cs_asl <- d_guess %>% 
  filter(ewma_param == "cs", condition == "ASL", rt <= asl_cut) %>% 
  pull(mean_param)

ucl_asl <- d_guess %>% 
  filter(ewma_param == "ucl", condition == "ASL", rt <= asl_cut) %>% 
  pull(mean_param)

AUC_CS_asl = trapz(rt_asl, cs_asl)
AUC_UCL_asl = trapz(rt_asl, ucl_asl)

# difference
diff_asl <- AUC_UCL_asl - AUC_CS_asl
```

```{r}
rt_face <- d_guess %>% 
  filter(ewma_param == "cs", condition == "Face", rt <= face_cut) %>% 
  pull(rt)

cs_face <- d_guess %>% 
  filter(ewma_param == "cs", condition == "Face", rt <= face_cut) %>% 
  pull(mean_param)

ucl_face <- d_guess %>% 
  filter(ewma_param == "ucl", condition == "Face", rt <= face_cut) %>% 
  pull(mean_param)

AUC_CS_face = trapz(rt_face, cs_face)
AUC_UCL_face = trapz(rt_face, ucl_face)

# difference
diff_face <- AUC_UCL_face - AUC_CS_face
```

```{r}
plot_grid(ewma_boxplots$trio, curves_plot)
```

how to compare this to boxplot?

```{r}
diff_asl < diff_face
```


```{r}
d_guess %>% 
  mutate(dt = c(diff(rt), mean(diff(rt)))) %>%
  spread(ewma_param, mean_param) %>% 
  mutate(guess_diff = ifelse(cs < ucl, ucl - cs, 0), 
         signal_diff = ifelse(cs > ucl, cs - ucl, 0)) %>% 
  group_by(condition) %>% 
  summarise(auc_guess = sum(guess_diff * dt), 
            auc_signal = sum(signal_diff * dt)) %>%
  mutate(guess_ratio = auc_guess / (auc_guess + auc_signal), 
         signal_ratio = 1-guess_ratio)
```

### Experiment 2: Text (Adults)

```{r}
ewma_control_charts$text
```

### Experiment 3: Noise and Gaze (kids)

```{r, fig.width = 9, fig.height = 4}
cowplot::plot_grid(ewma_control_charts$noise, ewma_control_charts$gaze, 
                   ncol = 2)
```

### Experiment 3: Noise and Gaze (adults)

```{r}
emwa_ng <- d %>% 
  filter(rt <= 0.8, experiment == "noise_gaze") %>% 
  aggregate_ewma() %>% 
  plot_ewma_chart()
```

```{r}
adult_noise_control <- d %>% 
  filter(rt <= 1, experiment == "noise_gaze") %>% 
  mutate(gaze_condition = ifelse(str_detect(condition, "gaze"), "gaze", 
                                 "straight_ahead"),
         noise_condition = ifelse(str_detect(condition, "noise"), "noise", "clear")) %>% 
  mutate(condition = noise_condition) %>%
  aggregate_ewma() %>% 
  plot_ewma_chart() +
  facet_wrap(~condition, ncol = 2) +
  ylim(0.4, 1) +
  xlim(0,1.4) 
```

```{r}
kid_noise_control <- ewma_control_charts$noise +
  ylim(0.4, 1) +
  xlim(0,1.4) +
  facet_wrap(~condition, ncol = 2)
```

```{r}
plot_grid(kid_noise_control, adult_noise_control, ncol = 1)
```

Save control charts.

```{r save_control_charts, eval = F}
# text
ggsave(plot = ewma_control_charts$text, 
       filename = paste0(plot.save.path, "e2_control_chart.png"), 
       width = 3, height = 3.5)

# noise gaze adults
ggsave(plot = ewma_control_charts$noise_gaze, 
       filename = paste0(plot.save.path, "adult_ng_control_chart.png"), 
       width = 3, height = 3.5)

# trio kids
ggsave(plot = ewma_control_charts$trio, 
       filename = paste0(plot.save.path, "e1_control_chart.png"), 
       width = 3, height = 3.5)
```

## Visualize EWMA results: Proportion guessing boxplots 

Make all the boxplots for each experiment using my own EWMA helper function. 

```{r}
ewma_boxplots <- d %>% 
  #filter(rt <= 1.5) %>% 
  split(.$experiment) %>% 
  purrr::map(.f = make_ewma_boxplot)
```

Put all the boxplots together. 

### Experiment 1: Trio (kids)

```{r, fig.height = 4}
ewma_boxplots$trio 
```

### Experiment 2: Text (Adults)

```{r, fig.height = 4}
ewma_boxplots$text
```

### Experiment 3: Noise and Gaze (kids)

```{r, fig.height = 4}
cowplot::plot_grid(ewma_boxplots$noise, ewma_boxplots$gaze, ncol = 2) 
```

```{r}
kid_noise_box <- ewma_boxplots$noise
```

### Experiment 3: Noise and Gaze (adults)

```{r, fig.height = 4}
adult_noise_box <- d %>% 
  filter(rt <= 4, experiment == "noise_gaze") %>% 
  mutate(gaze_condition = ifelse(str_detect(condition, "gaze"), "gaze", 
                                 "straight_ahead"),
         noise_condition = ifelse(str_detect(condition, "noise"), "noise", "clear")) %>% 
  mutate(condition = noise_condition) %>%
  make_ewma_boxplot()
```


```{r}
plot_grid(kid_noise_box, adult_noise_box, ncol = 1)
```

