---
title: "Speed-Acc-Novel Shifts Analysis"
output: html_document
---

## Set up

```{r chunk_options, echo = F}
# set some global options
knitr::opts_chunk$set(warning=F, message=F, sanitize = T, echo=T, cache = F)
```

Libraries and data paths
```{r}
library(here)
library(tidyverse)
library(knitr)
library(lme4)
# source(here::here("code/helper_functions/libraries_and_functions.R"))
data_path <- "data/03_processed_data/"
theme_set(ggthemes::theme_base())
```

Read in data
```{r}
d <- read_csv(here::here(data_path, "speed_acc_novel_shifts.csv")) %>% 
  mutate(learn_block_half = ifelse(trial_num_learn_block <= 2, "first", "second"),
         trial_num_lblock_8 = case_when(
           trial_type == "exposure" & trial_num_learn_block == 1 ~ "1",
           trial_type == "test" & trial_num_learn_block == 1 ~ "2",
           trial_type == "exposure" & trial_num_learn_block == 2 ~ "3",
           trial_type == "test" & trial_num_learn_block == 2 ~ "4",
           trial_type == "exposure" & trial_num_learn_block == 3 ~ "5",
           trial_type == "test" & trial_num_learn_block == 3 ~ "6",
           trial_type == "exposure" & trial_num_learn_block == 4 ~ "7",
           trial_type == "test" & trial_num_learn_block == 4 ~ "8",
           TRUE ~ "NA"
         ),
         correct_bool = ifelse(shift_accuracy == "correct", TRUE, FALSE))
```

## Check the data

Number of unique participants

```{r}
d$subid %>% unique() %>%length()
```

Group by demographics

```{r}
d_by_subject <- d %>%
  group_by(subid, gender, ethnicity_race, order_key, keep_drop, 
           reason_excluded, age, age_category, age_group) %>%
  summarise()
```

Adults vs. children and gender breakdown. 

```{r}
d_by_subject %>%
  filter(keep_drop == "keep") %>% 
  group_by(age_category, gender) %>%
  count(age_category)
```

Count the number of participants who are kept and dropped

```{r}
d_by_subject %>%
  group_by(keep_drop) %>%
  count(keep_drop)
```

Make exclusions table

```{r}
d_by_subject %>%
  group_by(reason_excluded) %>%
  count(reason_excluded, sort = T) %>% 
  na.omit() %>% 
  kable()
```

Count trials per gaze condition

```{r}
d %>%
  group_by(gaze_condition) %>%
  count(gaze_condition)
```

## Filter data

Remove shifts that do not start at center. Remove participants based on keep_drop, and extreme RTs. Take out word blocks for reasons explained in subject log or if there is data for less than 50% of word block:

```{r}
d_keep <- d %>%
  filter(is.na(block_excluded) | 
           block_excluded != learning_block, 
         shift_start_location == "center") %>%
  group_by(subid, learning_block) %>%
  mutate(n_trials = n()) %>% 
  filter(n_trials >= 4,
         rt > 0,
         keep_drop == "keep", 
         shift_start_location == "center") %>% 
  ungroup()
```

Count number of trials after filtering

```{r}
d_keep %>% count(subid, gaze_condition, trial_type, trial_num_learn_block)
```

Filter extreme RTs

```{r}
m_rt <- log(d_keep$rt) %>% mean()
sd_rt <- log(d_keep$rt) %>% sd()

d_keep <- d_keep %>% 
  mutate(log_rt = log(rt),
         keep_rt = case_when(
           log_rt <= m_rt + 3*sd_rt & log_rt >= m_rt - 3*sd_rt ~ "keep",
           TRUE ~ "drop"
         ))
```

How many trials get filtered for extreme RTs?

```{r}
d_keep %>% ungroup %>% count(keep_rt)
```

## RT analysis

For both children and adults, plot RT as a function of trial number, trial type, and gaze condition.

```{r make key RT plot}
ss_rt <- d_keep %>%
  filter(!is.na(rt), keep_rt == "keep") %>%
  group_by(subid, 
           age_category,
           gaze_condition, 
           trial_type, 
           trial_num_learn_block) %>%
  summarise(m_ss = mean(rt), n_trials = n()) 

ms_rt <- ss_rt %>%
  group_by(age_category,
           gaze_condition, 
           trial_type, 
           trial_num_learn_block) %>%
  tidyboot::tidyboot_mean(column = m_ss, nboot = 1000)

ms_rt %>% 
  ungroup() %>% 
  mutate(age_category = factor(age_category, levels = c("child", "adult"))) %>% 
  ggplot(mapping = aes(x = trial_num_learn_block,
                       y = mean,
                       color = gaze_condition, 
                       group = interaction(gaze_condition))) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = 0.2)) +
  geom_line(position = position_dodge(width = 0.2)) +
  lims(y = c(0, 2.5)) +
  facet_grid(age_category ~ trial_type) +
  labs(x = "trial number", 
       y = "mean RT (sec)",
       title = "First shift reaction time") +
  theme_minimal() +
  theme(text = element_text(size = 14), 
        panel.border = element_rect(size = 1, color = "grey", fill = NA),
        legend.position = "top")
```

### Collapse across first/second half of word block

```{r make key RT plot}
ss_rt <- d_keep %>%
  filter(!is.na(rt), keep_rt == "keep") %>%
  group_by(subid, 
           age_category,
           gaze_condition, 
           trial_type, 
           learn_block_half,
           age) %>%
  summarise(m_ss = mean(rt), n_trials = n()) 

ms_rt <- ss_rt %>%
  group_by(age_category,
           gaze_condition, 
           trial_type, 
           learn_block_half) %>%
  tidyboot::tidyboot_mean(column = m_ss, nboot = 1000)

ms_rt %>% 
  ungroup() %>% 
  mutate(age_category = factor(age_category, levels = c("child", "adult"))) %>% 
  ggplot(mapping = aes(x = learn_block_half,
                       y = mean,
                       color = gaze_condition, 
                       group = interaction(gaze_condition))) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = 0.2)) +
  geom_line(position = position_dodge(width = 0.2)) +
  lims(y = c(0, 2)) +
  facet_grid(age_category ~ trial_type) +
  labs(x = "trial number", 
       y = "mean RT (sec)",
       title = "First shift reaction time") +
  theme_minimal() +
  theme(text = element_text(size = 14), 
        panel.border = element_rect(size = 1, color = "grey", fill = NA),
        legend.position = "top")
```

### Plot RT over all 8 trials in learning block

```{r}
ss_rt <- d_keep %>%
  ungroup() %>% 
  filter(!is.na(rt), keep_rt == "keep") %>%
  group_by(subid, 
           age_category,
           gaze_condition, 
           trial_num_lblock_8) %>%
  summarise(m_ss = mean(rt), n_trials = n()) 

ms_rt <- ss_rt %>%
  group_by(age_category,
           gaze_condition, 
           trial_num_lblock_8) %>%
  tidyboot::tidyboot_mean(column = m_ss, nboot = 1000)

ms_rt %>% 
  ungroup() %>% 
  mutate(age_category = factor(age_category, levels = c("child", "adult"))) %>% 
  ggplot(mapping = aes(x = trial_num_lblock_8,
                       y = mean,
                       color = gaze_condition, 
                       group = interaction(gaze_condition))) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = 0.2)) +
  geom_line(position = position_dodge(width = 0.2)) +
  lims(y = c(0, 2)) +
  facet_grid(~age_category) +
  labs(x = "trial number", 
       y = "mean RT (sec)",
       title = "First shift reaction time") +
  theme_minimal() +
  theme(text = element_text(size = 14), 
        panel.border = element_rect(size = 1, color = "grey", fill = NA),
        legend.position = "top")
```

### Continuous age analyses

```{r}
d_keep %>% 
  filter(age_category == "child") %>% 
  group_by(subid, age, gaze_condition, trial_type) %>% 
  summarise(m_ss = mean(rt)) %>% 
  ggplot(aes(x = age, y = m_ss, color = gaze_condition)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = F, size = 1.5) +
  facet_grid(~trial_type) +
  ggthemes::scale_color_ptol()
``` 

### Accuracy

### Make key First Shift Accuracy plot. 

```{r}
ss_acc <- d_keep %>% 
  filter(keep_rt == "keep") %>% 
  group_by(subid, gaze_condition, trial_num_learn_block, age_category, trial_type) %>% 
  summarise(m_ss = mean(correct_bool), n_trials = n())  

ms_acc <- ss_acc %>% 
  group_by(gaze_condition, trial_type, trial_num_learn_block, age_category) %>% 
  tidyboot::tidyboot_mean(column = m_ss, nboot = 1000)

ggplot(data = ms_acc,
       mapping = aes(x = trial_num_learn_block,
                     y = mean,
                     color = gaze_condition, 
                     group = interaction(gaze_condition))) +
  geom_hline(yintercept = 0.5, lty = "dashed") +
  geom_line(position = position_dodge(width = 0.2)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = 0.2)) +
  scale_y_continuous(limits = c(0, 1.05)) +
  facet_grid(age_category ~ trial_type) +
  labs(x = "trial number", 
       y = "proportion correct",
       title = "First shift accuracy") +
  theme_minimal() +
  theme(text = element_text(size = 14), 
        panel.border = element_rect(size = 1, color = "grey", fill = NA),
        legend.position = "top")
```

### Summarise accuracy collapsing across blocks 

```{r}
ss_acc_half <- d_keep %>% 
  filter(keep_rt == "keep") %>% 
  mutate(correct_bool = ifelse(shift_accuracy == "correct", TRUE, FALSE)) %>% 
  group_by(subid, gaze_condition, learn_block_half, age_category, trial_type) %>% 
  summarise(m_ss = mean(correct_bool), n_trials = n())  
  
ms_acc_half <- ss_acc_half %>% 
  group_by(gaze_condition, trial_type, learn_block_half, age_category) %>% 
  tidyboot::tidyboot_mean(column = m_ss, nboot = 1000)

ggplot(data = ms_acc_half,
       mapping = aes(x = learn_block_half,
                     y = mean,
                     color = gaze_condition, 
                     group = interaction(gaze_condition))) +
  geom_hline(yintercept = 0.5, lty = "dashed") +
  geom_line(position = position_dodge(width = 0.2)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = 0.2)) +
  scale_y_continuous(limits = c(0, 1.05)) +
  facet_grid(age_category ~ trial_type) +
  labs(x = "half of learning block", 
       y = "proportion correct",
       title = "First shift accuracy") +
  theme_minimal() +
  theme(text = element_text(size = 14), 
        panel.border = element_rect(size = 1, color = "grey", fill = NA),
        legend.position = "top")
```

### Summarise accuracy collapsing across time

```{r}
ss_acc_cond <- d_keep %>% 
  filter(keep_rt == "keep") %>% 
  group_by(subid, gaze_condition, age_category, trial_type) %>% 
  summarise(m_ss = mean(correct_bool), n_trials = n())  

ms_acc_cond <- ss_acc_half %>% 
  group_by(gaze_condition, trial_type, age_category) %>% 
  tidyboot::tidyboot_mean(column = m_ss, nboot = 1000)

ggplot(data = ms_acc_cond,
       mapping = aes(x = fct_rev(age_category),
                     y = mean,
                     color = gaze_condition, 
                     group = interaction(gaze_condition))) +
  geom_hline(yintercept = 0.5, lty = "dashed") +
  geom_line(position = position_dodge(width = 0.2)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = 0.2)) +
  scale_y_continuous(limits = c(0, 1.05)) +
  facet_grid(~ trial_type) +
  labs(x = "age group", 
       y = "proportion correct",
       title = "First shift accuracy") +
  theme_minimal() +
  theme(text = element_text(size = 14), 
        panel.border = element_rect(size = 1, color = "grey", fill = NA),
        legend.position = "top")
```
### Models

First shift Acc.

```{r}
m1 <- d_keep %>% 
  filter(keep_rt == "keep") %>% 
  glmer(data = ., 
        correct_bool ~ gaze_condition * trial_type + age_category + (gaze_condition|subid),
        family = 'binomial')

summary(m1)
```

First shift RT

```{r}
m2 <- d_keep %>% 
  filter(keep_rt == "keep") %>% 
  lmer(data = ., 
     log(rt) ~ gaze_condition * trial_type + age_category + (gaze_condition|subid) + (trial_type|subid)
     )

summary(m2)
```