---
title: "Speed-Acc Novel Timecourse"
output: html_document
---

```{r chunk_options, echo = F}
knitr::opts_chunk$set(warning=F, message=F, sanitize = T, echo=T, cache = F)
```

## Set up

```{r}
source(here::here("code/helper_functions/libraries_and_functions.R"))
data_path <- "data/03_processed_data/novel_words"
theme_set(ggthemes::theme_base())
```

## Read data

```{r read test data, eval = F}
# for running code on test data
file_name <- "speed_acc_novel_timecourse_test.feather" 
d <- read_feather(here::here("data/test_data/", file_name)) 
d %<>% mutate(keep_drop = "keep", age_category = "adult")
```

Read data

```{r}
file_name <- "speed_acc_novel_timecourse.feather"
d <- read_feather(here::here(data_path, file_name)) 
```

Filter based on exlcusions in the subject log and remove bad blocks based on subject log.

```{r}
d_analysis <- d %>% 
  filter(keep_drop == "keep",
         t_rel_noun >= 0, 
         t_rel_noun <= 3
        )
```

Create time bins for each participant and each trial. 

```{r}
d_analysis %<>% 
  split(.$subid) %>%  
  purrr::map_dfr(create_time_bins_ss, t_ms_diff = 33)
```

Create exclusions table.

```{r}
d %>% 
  distinct(subid, keep_drop, reason_excluded, age_category) %>% 
  filter(keep_drop == "drop") %>% 
  kable()
```

Create exclusions list based on number of trials completed.

```{r}
ss_exclude <- d_analysis %>%
  filter(target_looking != "away") %>% 
  distinct(subid, trial_num_exp) %>% 
  count(subid) %>% 
  filter(n < 16) %>% 
  pull(subid)

ss_exclude
```

Filter participants who did not complete more than half the trials. 

```{r}
d_analysis %<>% filter(!(subid %in% ss_exclude))
```

Check how many trials in each block.

```{r}
d_analysis %>% 
  distinct(subid, trial_num_exp, learning_block, gaze_condition) %>% 
  count(subid, learning_block, gaze_condition) %>% 
  arrange(n) %>% 
  kable()
```

Make a table of proportion looking to each area of interest: Left, Right, Center, and Away

```{r}
d_analysis %>% 
  filter(!is.na(target_looking)) %>% 
  group_by(target_looking, age_category) %>% 
  summarise(count_looks = n()) %>% 
  group_by(age_category) %>% 
  mutate(total_looks = sum(count_looks),
         prop_looks = round(count_looks / total_looks, 2)) %>% 
  arrange(age_category) %>% 
  kable()
```

Create flag for trials with less than half valid samples.

```{r}
trial_filter <- d_analysis %>% 
  distinct(subid, trial_num_exp, learning_block, gaze_condition, target_looking, time_ms_normalized) %>% 
  count(subid, trial_num_exp, learning_block, gaze_condition, target_looking) %>% 
  group_by(trial_num_exp, subid) %>% 
  mutate(total_samples = sum(n),
         prop_trial = n / total_samples,
         good_trial = case_when(
           target_looking == "away" & prop_trial >= 0.5 ~ "drop",
           TRUE ~ "keep"
         )) %>% 
  distinct(subid, trial_num_exp, good_trial)

d_analysis %<>% left_join(trial_filter)
```

Check how many samples we have for each trial after removing away looks.

```{r}
d_analysis %<>% filter(target_looking != "away")
```

```{r}
n_samples_trial <- d_analysis %>% 
  count(subid, trial_num_exp) %>% 
  rename(n_samples_trial = n)
  
n_samples_trial %>%   
  ggplot(aes(x = n_samples_trial)) +
  geom_histogram() 

d_analysis %<>% left_join(n_samples_trial)
```

Filter away looks and bad trials (< 50% looking away).

```{r}
d_analysis %<>% 
  filter(good_trial == "keep") %>% 
  filter(n_samples_trial >= 45)
```

## Visualize timecourse looking to all AOIs

```{r compute mean gaze onset relative to noun onset}
gaze_onset <- d_analysis %>% 
  distinct(noun_onset_seconds, gaze_onset_seconds) %>% 
  na.omit() %>% 
  mutate(gaze_onset_rel_noun = (gaze_onset_seconds - noun_onset_seconds) * 1000) %>% 
  summarise(m_gaze_onset = mean(gaze_onset_rel_noun))
```

### timecourse as a function of trial number in block

```{r, eval = F}
ss_groupings <- list("subid", "time_ms_normalized", "gaze_condition", "trial_type",
                     "age_category", "trial_num_exp")

ms_groupings <- list("subid", "time_ms_normalized", "gaze_condition", "trial_type", 
                     "age_category")

ms_time <- aggregate_ss_looking(d_analysis, ss_groupings, ms_groupings, aoi_column = "target_looking") 

# Make timecourse plot
ms_time %>% 
  filter(age_category == "adult") %>%  
  plot_timecourse(facet_type = "age_category~trial_type") +
  geom_vline(xintercept = gaze_onset$m_gaze_onset, lty = "dashed") +
  scale_color_manual(values = c("darkblue", "red", "darkgreen"))
```

### timecourse as a function of order

```{r, eval = F}
ss_order_groups <- list("subid", "time_ms_normalized", "gaze_condition", "trial_type",
                     "age_category","trial_num_exp", "order_name")

ms_order_groups <- list("subid", "time_ms_normalized", "gaze_condition", "trial_type", 
                     "age_category" , "order_name")

ms_order <- aggregate_ss_looking(d_analysis, ss_order_groups, ms_order_groups, aoi_column = "target_looking") 

# Make timecourse plot
ms_order %>% 
  filter(age_category == "adult") %>%  
  plot_timecourse(facet_type = "order_name~trial_type")
```

### timecourse as a function of trial number in the learning block

```{r, eval = F}
ss_order_lblock <- list("subid", "time_ms_normalized", "gaze_condition", "trial_type",
                     "age_category","trial_num_exp", "learning_block")

ms_order_lblock <- list("subid", "time_ms_normalized", "gaze_condition", "trial_type", 
                     "age_category" , "learning_block")

ms_lblock <- aggregate_ss_looking(d_analysis, ss_order_lblock, ms_order_lblock, aoi_column = "target_looking") 

# Make timecourse plot
ms_lblock %>% 
  filter(age_category == "adult") %>%  
  plot_timecourse(facet_type = "learning_block~trial_type")
```

### Timecourse by gaze block number (whether you got gaze or straight ahead first).

```{r, eval = F}
ss_groupings_block <- list("subid", "time_ms_normalized", "gaze_condition", "trial_type", "age_category", "gaze_block", "trial_num_exp")
ms_groupings_block <- list("subid", "time_ms_normalized", "gaze_condition", "trial_type", "age_category",  "gaze_block")
ms_time_block <- aggregate_ss_looking(d_analysis, ss_groupings_block, ms_groupings_block, aoi_column = "target_looking") 

# Plot timecourse by block
ms_time_block %>% 
  filter(age_category == "adult") %>% 
  plot_timecourse(facet_type = "gaze_block~trial_type")
```

## Aggregated proportion looking plots

### How does looking to target change across trials within a learning block?

```{r}
ss_groupings_tr_num <- list("subid", "gaze_condition", "trial_type", "trial_num_learn_block", "age_category", "trial_num_exp")
ms_groupings_tr_num <- list("subid", "gaze_condition", "trial_type", "trial_num_learn_block", "age_category")

ms_trials <- d_analysis %>% 
  filter(target_looking %in% c("target", "distracter")) %>% 
  aggregate_ss_looking(ss_groupings_tr_num, ms_groupings_tr_num,
                       aoi_column = "target_looking", 
                       use_bootstrap = TRUE, 
                       n_boot = 1000) 

# Make key plot of target looking as a function of trial number and trial type.
ms_trials %>% 
  ungroup() %>% 
  mutate(age_category = factor(age_category, levels = c("child", "adult"))) %>% 
  filter(target_looking == "target") %>% 
  ggplot(aes(x = trial_num_learn_block, y = mean, 
             color = gaze_condition,
             group = interaction(target_looking, gaze_condition))) +
  geom_hline(yintercept = 0.5, lty = "dashed") +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.2)) +
  geom_line(position = position_dodge(width = 0.2)) +
  labs(x = "Trial Number",
       y = "Prop. looking to target",
       color = "Gaze condition:"
       #title = "Proportion Looking to Target Across Trials"
       ) +
  lims(y = c(0, 1.05)) +
  facet_grid(age_category~trial_type) +
  theme_minimal() + 
  #ggthemes::scale_color_ptol() +
  theme(legend.position = "top",
        panel.border = element_rect(colour = "grey", fill=NA, size=1),
        text = element_text(size = 14))
```

### How does looking to target change across blocks in the experiment?

```{r}
ss_groupings_block <- list("subid", "gaze_condition", "trial_type", "learning_block", "age_category", "trial_num_exp")
ms_groupings_block <- list("subid", "gaze_condition", "trial_type", "learning_block", "age_category")

ms_blocks <- d_analysis %>% 
  filter(target_looking != "center") %>% 
  aggregate_ss_looking(ss_groupings_block, ms_groupings_block,
                       aoi_column = "target_looking", 
                       use_bootstrap = TRUE, 
                       n_boot = 1000) 

# Make key plot of target looking as a function of trial number and trial type.
ms_blocks %>% 
  ungroup() %>% 
  mutate(age_category = factor(age_category, levels = c("child", "adult"))) %>% 
  filter(target_looking == "target") %>% 
  ggplot(aes(x = learning_block, y = mean, 
             color = gaze_condition,
             group = interaction(target_looking, gaze_condition))) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.2)) +
  geom_line(position = position_dodge(width = 0.2)) +
  labs(x = "Block Number",
       y = "Prop. looking to target",
       color = "Gaze condition:"
      # title = "Proportion Looking to Target Across Word Blocks"
      ) +
  lims(y = c(0.1, 1.05)) +
  facet_grid(age_category~trial_type) +
  geom_hline(yintercept = 0.5, lty = "dashed") +
  #ggthemes::scale_color_ptol() +
  theme_minimal() +
  theme(legend.position = "top",
        panel.border = element_rect(colour = "grey", fill=NA, size=1),
        text = element_text(size = 14))
```

### How does looking to target change across trials within a gaze block?

```{r}
ss_groupings_gblock <- list("subid", "gaze_condition", "trial_type", "trial_num_gaze_block", "age_category", "trial_num_exp")
ms_groupings_gblock <- list("subid", "gaze_condition", "trial_type", "trial_num_gaze_block", "age_category")

ms_gblock <- d_analysis %>% 
  filter(target_looking != "center") %>% 
  aggregate_ss_looking(ss_groupings_gblock, ms_groupings_gblock,
                       aoi_column = "target_looking", 
                       use_bootstrap = TRUE, 
                       n_boot = 1000) 

# Make key plot of target looking as a function of trial number and trial type.
ms_gblock %>% 
  filter(target_looking == "target") %>% 
  ggplot(aes(x = trial_num_gaze_block, y = mean, 
             color = gaze_condition,
             group = interaction(target_looking, gaze_condition))) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.2)) +
  geom_line(position = position_dodge(width = 0.2)) +
  labs(x = "Trial Number",
       y = "Proportion looking",
       color = "Gaze condition:",
       title = "Proportion Looking to Target Across Gaze Block") +
  lims(y = c(0.1, 1.05)) +
  facet_grid(age_category~trial_type) +
  geom_hline(yintercept = 0.5, lty = "dashed") +
  #ggthemes::scale_color_ptol() +
  theme(legend.position = "top")
```

### How does looking to target change depending on order of gaze/no-gaze block?

```{r}
ss_groupings_block_order <- list("subid", "gaze_condition", "trial_type", "gaze_block", 
                                 "trial_num_learn_block", "age_category", "trial_num_exp")
ms_groupings_block_order <- list("subid", "gaze_condition", "trial_type",  "gaze_block",
                                 "trial_num_learn_block", "age_category")

ms_block_order <- d_analysis %>% 
  filter(target_looking != "center") %>% 
  aggregate_ss_looking(ss_groupings_block_order, ms_groupings_block_order,
                       aoi_column = "target_looking", 
                       use_bootstrap = TRUE, 
                       n_boot = 1000) 

# Make key plot of target looking as a function of trial number and trial type.
ms_block_order %>% 
  filter(target_looking == "target") %>% 
  ggplot(aes(x = trial_num_learn_block, y = mean, 
             lty = as.factor(gaze_block),
             color = gaze_condition,
             group = interaction(target_looking, gaze_condition, gaze_block))) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.2)) +
  geom_line(position = position_dodge(width = 0.2)) +
  labs(x = "Trial Number",
       y = "Proportion looking",
       color = "Gaze condition:",
       title = "Proportion Looking to Target Across Trials") +
  lims(y = c(0.1, 1.05)) +
  facet_grid(age_category~trial_type) +
  geom_hline(yintercept = 0.5, lty = "dashed") +
  ggthemes::scale_color_ptol() +
  theme(legend.position = "top")
```

### Do participants look more to the target in the gaze condition?

```{r}
ss_groupings_cond <- list("subid", "gaze_condition", "trial_type", "age_category", "trial_num_exp")
ms_groupings_cond <- list("subid", "gaze_condition", "trial_type", "age_category")

ms_cond <- d_analysis %>% 
  filter(target_looking != "center") %>% 
  aggregate_ss_looking(ss_groupings_cond, ms_groupings_cond,
                       aoi_column = "target_looking", 
                       use_bootstrap = TRUE, 
                       n_boot = 1000) 
# Plot
ms_cond %>% 
  filter(target_looking == "target") %>% 
  ggplot(aes(x = trial_type, y = mean, 
             color = gaze_condition,
             group = interaction(gaze_condition))) +
  geom_hline(yintercept = 0.5, lty = "dashed") +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.2),
                  size = 0.7) +
  geom_line(position = position_dodge(width = 0.2)) +
  lims(y = c(0.1, 1.1)) +
  labs(x = "Age Group", y = "Prop. Looking Target", color = "Gaze Condition:") + 
  facet_grid(~age_category) +
 # ggthemes::scale_color_ptol() +
  theme(text = element_text(size = 11), legend.position = "top")
```

### How does looking to the speaker change across trials within learning block?

```{r}
ss_groupings_tr_num_center <- list("subid", "gaze_condition", "trial_type", "age_category", "trial_num_exp", "trial_num_learn_block")
ms_groupings_tr_num_center <- list("subid", "gaze_condition", "trial_type", "age_category", "trial_num_learn_block")

ms_trial_num_center <- d_analysis %>% 
  aggregate_ss_looking(ss_groupings_tr_num_center, ms_groupings_tr_num_center,
                       aoi_column = "target_looking", 
                       use_bootstrap = TRUE, 
                       n_boot = 1000) 

# Make key plot of target looking as a function of trial number and trial type.
ms_trial_num_center %>% 
  ungroup() %>% 
  mutate(age_category = factor(age_category, levels = c("child", "adult"))) %>% 
  filter(target_looking == "center") %>% 
  ggplot(aes(x = trial_num_learn_block, y = mean, 
             #lty = as.factor(gaze_block),
             color = gaze_condition,
             group = interaction(target_looking, gaze_condition))) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  position = position_dodge(width = 0.2)) +
  geom_line(position = position_dodge(width = 0.2)) +
  labs(x = "Trial Number",
       y = "Prop. looking to speaker",
       color = "Gaze condition:"
       #title = "Proportion Looking to Speaker Across Trials"
       ) +
  lims(y = c(0, 0.9)) +
  facet_grid(age_category~trial_type) +
  geom_hline(yintercept = 0.33, lty = "dashed") +
  #ggthemes::scale_color_ptol() +
  theme_minimal() +
  theme(legend.position = "top",
        panel.border = element_rect(colour = "grey", fill=NA, size=1),
        text = element_text(size = 14))
```

## Statistical models

```{r}
ss_models_groups <- list("subid", "gaze_condition", "trial_type", "age_category","trial_num_exp","trial_num_learn_block", "target_word")

ss_models <- d_analysis %>% 
  filter(target_looking != "center") %>% 
  aggregate_ss_looking(ss_grouping_cols = ss_models_groups, aoi_column = "target_looking", return_ss_df = TRUE) 
```

Quick and dirty lmers

```{r, eval = F}
m_exposure <- ss_models %>% 
  filter(target_looking == "target", trial_type == "exposure") %>% 
  lmer(data = ., 
       prop_looking ~ (gaze_condition + age_category + trial_num_learn_block)^2 + (gaze_condition|subid))

summary(m_exposure)
```

```{r, eval = F}
m_test <- ss_models %>% 
  filter(target_looking == "target", trial_type == "test") %>% 
  lmer(data = ., 
       prop_looking ~ (gaze_condition + age_category + trial_num_learn_block)^2 + (gaze_condition|subid))

summary(m_test)
```