---
title: "Speed-acc-familiar BDA"
output: html_document
---

## Setup

This document contains the codebase for the bayesian data analysis of the Gaze experiment mentioned in the paper, "An information-seeking account of children's eye movements during grounded signed and spoken language comprehension."

```{r set global_options, include=FALSE}
source(here::here("code/helper_functions/libraries_and_functions.R"))
source(here::here("code/helper_functions/ewma_helper_funs.R"))

data_path <- "data/03_processed_data/familiar_words/"
models_path <- "data/04_model_outputs/"

options(mc.cores=parallel::detectCores())
set.seed (3875)
```

```{r read data}
d_kids_gaze <- read_csv(here::here(data_path, "speed_acc_child_gaze_fstshift_tidy.csv")) 
d_adults <- read_csv(here::here(data_path, "speed_acc_adult_ng_fstshift_tidy.csv")) 

# clean datasets and merge
d_adults %<>% select(-age)

d_kids_gaze %<>% mutate(noise_condition = ifelse(noise_condition == "no_noise", 
                                                 "clear", 
                                                 noise_condition))

d <- bind_rows(mutate(d_kids_gaze, experiment = "kids_gaze", age_category = "children"),
               mutate(d_adults, experiment = "adults_ng", age_category = "adults")) %>% 
  select(-resp_onset_type_fact, -subid_short) %>% 
  mutate(age_category = factor(age_category) %>% fct_rev()) 

# test that we have the right number of rows after the merge (result should be TRUE)
nrow(d_kids_gaze) + nrow(d_adults) == nrow(d)
```

## RT and Accuracy models

```{r filter gaze experiment, eval = F}
d_model <- d %>% 
  filter(experiment != "kids_noise",
         keep_runsheet %in% c("yes", "keep"), 
         #keep_et == "include",
         noise_condition == "clear")

d_model %<>%
  filter(rt <= 2,
         response_onset_type == "noun",
         shift_start_location == "center") %>% 
  mutate(shift_acc_num = ifelse(shift_accuracy_clean == "correct", 1, 0),
         log_rt = log(rt))
```

### Accuracy (Gaze)

```{r fit acc gaze model, eval = T, message=FALSE}
m_bglm_acc_e2 <- stan_glmer(
  shift_acc_num ~ gaze_condition + age_category + (gaze_condition | subid) + (gaze_condition | target_image), 
  data = d_model,
  family = binomial(link = "logit"), 
  prior = normal(0, 2),
  prior_intercept = normal(0, 1),
  prior_covariance = decov(regularization = 2),
  chains = 4
)
```

### RT (Gaze)

```{r fit rt gaze model, eval = F}
m_bglm_rt_e2 <- stan_glmer(
  log_rt ~ gaze_condition + age_category + (gaze_condition | subid) + (gaze_condition | target_image), 
  family = gaussian(),
  data = d_model,
  prior = normal(0, 2), 
  prior_intercept = normal(0, 5),
  prior_covariance = decov(regularization = 2),
  chains = 4
)
```

### Extract posterior samples gaze experiment

```{r extract posterior samples gaze model}
# get posterior samples
samples_e2_acc <- m_bglm_acc_e2 %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  dplyr::rename(gaze_children = `(Intercept)`,
                straightahead_beta = gaze_conditionstraight_ahead,
                age_beta = age_categoryadults) %>% 
  select(gaze_children, straightahead_beta, age_beta)

samples_e2_rt <- m_bglm_rt_e2 %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  dplyr::rename(gaze_children = `(Intercept)`,
                straightahead_beta = gaze_conditionstraight_ahead,
                age_beta = age_categoryadults) %>% 
  select(gaze_children, straightahead_beta, age_beta)

# tidy up accuracy
samples_e2_acc_tidy <- samples_e2_acc %>% 
  mutate(straightahead_children = gaze_children + straightahead_beta,
         straightahead_adults = gaze_children + age_beta + straightahead_beta, 
         gaze_adults = gaze_children + age_beta,
         sample_id = 1:n()) %>% 
  gather(key = condition, value = param_est, -sample_id, -straightahead_beta, -age_beta) %>% 
  mutate(acc_prob_scale = logit_to_prob(param_est)) %>% 
  separate(condition, into = c("gaze_condition", "age_category"))

# tidy up rt samples
samples_e2_rt_tidy <- samples_e2_rt %>% 
    mutate(straightahead_children = gaze_children + straightahead_beta,
         straightahead_adults = gaze_children + age_beta + straightahead_beta, 
         gaze_adults = gaze_children + age_beta,
         sample_id = 1:n()) %>% 
  gather(key = condition, value = param_est, -sample_id, -straightahead_beta, -age_beta) %>% 
  mutate(rt_ms_scale = exp(param_est)) %>% 
  separate(condition, into = c("gaze_condition", "age_category"))
```

## EWMA models

Read in EWMA output. 

```{r read ewma output gaze, eval = F}
gaze_ewma_files <- c("speed_acc_kids_gaze_ewma_results.csv", "speed_acc_adult_ng_ewma_results.csv")
d_ewma_gaze <- gaze_ewma_files %>% purrr::map_df(read_ewma, path = here::here(models_path))
```

Filter to select just the gaze conditions.

```{r filter ewma results gaze, eval = F}
d_ewma_gaze %<>% 
  filter(experiment %in% c("gaze", "noise_gaze"),
         condition %in% c("gaze", 
                          "straight_ahead", 
                          "gaze_clear", 
                          "straight_ahead_clear")) %>% 
  mutate(gaze_condition = ifelse(str_detect(condition, "gaze"), "gaze", "straight_ahead"),
         age_category = ifelse(age_code == "child", "children", "adults")) 
```

```{r fit cutpoints model gaze, eval = F}
ss_cutoffs_gaze <- d_ewma_gaze %>% 
  filter(guess == "response") %>% 
  group_by(subid, gaze_condition, age_category) %>% 
  summarise_(cutoff = interp(~ min(x), x = as.name("rt"))) %>% 
  mutate(log_cut = log(cutoff))

# fit model
m_cutoffs_gaze <- stan_lm(cutoff ~ gaze_condition + age_category, 
                          data = ss_cutoffs_gaze,
                          prior = R2(0.75, what = "mean"),
                          adapt_delta = 0.99)

# get posterior samples
samples_ewma_cuts_gaze <- m_cutoffs_gaze %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  dplyr::rename(gaze_adults = `(Intercept)`,
                straightahead_beta = gaze_conditionstraight_ahead,
                age_beta = age_categorychildren) %>% 
  select(gaze_adults, straightahead_beta, age_beta) %>% 
  mutate(gaze_children = gaze_adults + age_beta,
         straightahead_children = gaze_children + straightahead_beta, 
         straightahead_adults = gaze_adults + straightahead_beta,
         sample_id = 1:n()) %>% 
  gather(key = condition, value = param_est, -sample_id, -straightahead_beta, -age_beta)
```

### EWMA guessing model (Gaze)

```{r fit ewma guessing model gaze, eval = F}
# fit model
m_guessing_gaze <- stan_glmer(
  guess_num ~ gaze_condition + age_category + (gaze_condition | subid),
  data = d_ewma_gaze,
  prior = normal(0, 2),
  prior_intercept = normal(0, 1),
  prior_covariance = decov(regularization = 2), 
  chains = 4)

# get posterior samples
samples_ewma_guess_gaze <- m_guessing_gaze %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  dplyr::rename(gaze_adults = `(Intercept)`,
                straightahead_beta = gaze_conditionstraight_ahead,
                age_beta = age_categorychildren) %>% 
  select(gaze_adults, straightahead_beta, age_beta) %>% 
  mutate(gaze_children = gaze_adults + age_beta,
         straightahead_children = gaze_adults + age_beta + straightahead_beta, 
         straightahead_adults = gaze_adults + straightahead_beta,
         sample_id = 1:n()) %>% 
  gather(key = condition, value = param_est, -sample_id, -straightahead_beta, -age_beta)
```

## Save samples 

```{r save samples from all models}
posteriors <- list(rt_gaze = samples_e2_rt_tidy,
                   acc_gaze = samples_e2_acc_tidy,
                   ewma_cuts_gaze = samples_ewma_cuts_gaze,
                   ewma_guess_gaze = samples_ewma_guess_gaze)

saveRDS(posteriors, file = here::here(models_path, "speed-acc-gaze-posterior-samples.rds"))
```