---
title             : "Children integrate social and statistical information to learn new words"
shorttitle        : "Integrating social and statistical information"

author: 
  - name          : "Kyle MacDonald"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "450 Serra Mall, Stanford, CA 94306"
    email         : "kylem4@stanford.edu"
  - name          : "Virginia Marchman"
    affiliation   : "1"
  - name          : "Michael C. Frank"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Stanford University"

authornote: |

abstract: |
  Abstract here
  
keywords          : "eye movements; grounded language learning; information-seeking; gaze following"
wordcount         : "X"
bibliography      : ["speed-acc.bib", "r-references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
source(here::here("code/helper_functions/paper_helpers.R"))
bib <- knitcitations::read.bibtex(here::here("writing/manuscript/speed-acc.bib"))
```

```{r analysis_preferences}
knitr::opts_chunk$set(fig.pos = '!t', fig.width = 6, fig.asp=0.8, out.width = "90%", 
                      cache = T, fig.path='figs/', fig.align = 'center',
                      echo=F, warning=F, cache=T, 
                      message=F, sanitize = T)
```

```{r data_paths}
demo_path <- "data/01_participant_logs/"
data_path <- "data/03_processed_data/"
image_path <- "writing/manuscript/figures/figs_output/"
```

# Introduction

# Experiment 1

```{r read_familiar_words_data}
d_fam_child <- read_csv(here::here(data_path, "familiar_words/speed_acc_child_gaze_fstshift_tidy.csv")) %>% 
  rename(age_days = age) %>% 
  mutate(age_group = as.character(age_group))

d_fam_adult <- read_csv(here::here(data_path, "familiar_words/speed_acc_adult_ng_fstshift_tidy.csv")) %>% 
  filter(noise_condition == "clear") %>% 
  rename(run_date = dot,
         comments = notes) %>% 
  select(-age, -resp_onset_type_fact, -reason_excluded) %>% 
  mutate(birthday = NA,
         age_group = "adult", 
         age_days = NA,
         run_date = lubridate::as_datetime(run_date))

# clean up and join kid and adult data
d_fam <- bind_rows(d_fam_child, d_fam_adult)
```

## Methods

### Participants

### Materials

### Procedure

## Results and Discussion

# Experiment 2A

```{r read_gaze_xsit_data}
d_gz_xsit <- read_csv(here::here(data_path, "novel_words/gaze_xsit_tidy_trial_level.csv"))
d_gz_xsit_tc <- read_csv(here::here(data_path, "novel_words/gaze_xsit_tidy_timecourse.csv"))
```

## Methods

### Participants

### Materials

### Procedure

## Results and Discussion

# Experiment 2B

```{r read_speed_novel_data}
d_novel <- 
```

## Methods

### Participants

### Materials

### Procedure

## Results and Discussion


# General Discussion

\newpage

# References

```{r create_r-references}
#r_refs(file = here::here("writing/r-references.bib"))
my_citations <- cite_r(file = here::here("writing/manuscript/r-references.bib"), 
                       pkgs = c("tidyverse", "rstanarm", "papaja", "here", "knitr"), 
                       withhold = FALSE,
                       footnote = TRUE)
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
